---
title: 'Animal nutrition journal report: The first half of 2018'
author: "ruminoreticulum@gmail.com"
date: "07/04/2018"
output:
  html_document:
    code_folding: hide
    df_print: paged
    fig_height: 6
    highlight: textmate
    theme: default
    toc: no
    toc_depth: 3
    toc_float: yes
---
```{r setup, echo=FALSE, include=FALSE}
options(warn=-1)

library(knitr)
library(ggplot2)
library(plotly)
library(dplyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(stringr)

theme_set(theme_bw(base_family="AppleGothic"))
```

A report is published for **a personal interesting** of the recent animal nutrition. The papers about *"animal nutrition"* which published at some SCI(E) journals were selected and analyzed. HTML scraping, data visualization, English-Korean translation, and report generation are automate process except sorting of the papers. Codes are available at https://github.com/YoungjunNa/journal_scraping 

# 1. List of journals
```{r echo=TRUE}
journal_list <- readxl::read_excel("journal_result_2018_123456.xlsx")
table <- table(journal_list$journal) %>% data.frame()
colnames(table) <- c("Journal","Articles")
kable(table)
ggplot(table, aes(x=Journal, y=Articles, fill=Journal)) + geom_col() + theme(axis.text.x=element_text(angle=45, hjust=1)) + scale_fill_brewer(palette="Set3")
```

# 2. List of papers
## 2.1. Review
```{r echo=TRUE}
results <- readxl::read_excel("journal_result_2018_123456.xlsx")
results <- results[,c(7,9,8,5,4,1,2,3,6)]
filter(results, type=="review")
```

## 2.2. Monogastric
```{r rows.print=100, echo=TRUE}
filter(results, type=="original article" & class=="monogastric")
```

## 2.3. Ruminant
```{r rows.print=100, echo=TRUE}
filter(results, type=="original article" & class=="ruminant")
```

# 3. Wordcloud analysis
## 3.1. Monogastric
```{r cols.print=6, rows.print=18, echo=TRUE}
wc <- readxl::read_excel("journal_result_2018_123456.xlsx")
#wc <- filter(wc, class == "ruminant")
wc <- filter(wc, class == "monogastric")
#wc <- filter(wc, str_detect(wc$subject,"supplement")==TRUE)

#WORDCLOUD
wc <- Corpus(VectorSource(wc$subject))

wc_data<-tm_map(wc,stripWhitespace)
wc_data<-tm_map(wc_data, removeWords, c("and"))

wc_data<-tm_map(wc_data, tolower)
wc_data<-tm_map(wc_data,removeNumbers)
wc_data<-tm_map(wc_data, removePunctuation)
wc_data<-tm_map(wc_data, removeWords, stopwords("english"))
wc_data<-tm_map(wc_data, removeWords, c("affect","effect","effects","and","the","our","that","for","are","also","more","has","must","have","should","this","with"))

tdm_wc<-TermDocumentMatrix(wc_data) #Creates a TDM
TDM1<-as.matrix(tdm_wc) #Convert this into a matrix format
v = sort(rowSums(TDM1), decreasing = TRUE) #Gives you the frequencies for every word

wordcloud(wc_data, max.words = Inf, min.freq = 1, random.order = FALSE, rot.per = 0.1, colors = brewer.pal(8, "Dark2")) 


## Term-Document
dtm <- TermDocumentMatrix(wc_data)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
d

```

## 3.2. Ruminant
```{r cols.print=6, rows.print=18, echo=TRUE}
wc <- readxl::read_excel("journal_result_2018_123456.xlsx")
wc <- filter(wc, class == "ruminant")
#wc <- filter(wc, class == "monogastric")
#wc <- filter(wc, str_detect(wc$subject,"supplement")==TRUE)

#WORDCLOUD
wc <- Corpus(VectorSource(wc$subject))

wc_data<-tm_map(wc,stripWhitespace)
wc_data<-tm_map(wc_data, removeWords, c("and"))

wc_data<-tm_map(wc_data, tolower)
wc_data<-tm_map(wc_data,removeNumbers)
wc_data<-tm_map(wc_data, removePunctuation)
wc_data<-tm_map(wc_data, removeWords, stopwords("english"))
wc_data<-tm_map(wc_data, removeWords, c("cattle","affect","effect","effects","and","the","our","that","for","are","also","more","has","must","have","should","this","with","which","dairy"))

tdm_wc<-TermDocumentMatrix(wc_data) #Creates a TDM
TDM1<-as.matrix(tdm_wc) #Convert this into a matrix format
v = sort(rowSums(TDM1), decreasing = TRUE) #Gives you the frequencies for every word

wordcloud(wc_data, max.words = Inf, min.freq = 1, random.order = FALSE, rot.per = 0.1, colors = brewer.pal(8, "Dark2")) 

## Term-Document
dtm <- TermDocumentMatrix(wc_data)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
d

```

## 3.3. Overall

```{r cols.print=6, rows.print=18, echo=TRUE}
wc <- readxl::read_excel("journal_result_2018_123456.xlsx")
#wc <- filter(wc, class == "ruminant")
#wc <- filter(wc, class == "monogastric")
#wc <- filter(wc, str_detect(wc$subject,"supplement")==TRUE)

#WORDCLOUD
wc <- Corpus(VectorSource(wc$subject))

wc_data<-tm_map(wc,stripWhitespace)
wc_data<-tm_map(wc_data, removeWords, c("and"))

wc_data<-tm_map(wc_data, tolower)
wc_data<-tm_map(wc_data,removeNumbers)
wc_data<-tm_map(wc_data, removePunctuation)
wc_data<-tm_map(wc_data, removeWords, stopwords("english"))
wc_data<-tm_map(wc_data, removeWords, c("affect","effect","effects","and","the","our","that","for","are","also","more","has","must","have","should","this","with","which","dairy"))

tdm_wc<-TermDocumentMatrix(wc_data) #Creates a TDM
TDM1<-as.matrix(tdm_wc) #Convert this into a matrix format
v = sort(rowSums(TDM1), decreasing = TRUE) #Gives you the frequencies for every word

wordcloud(wc_data, max.words = Inf, min.freq = 1, random.order = FALSE, rot.per = 0.1, colors = brewer.pal(8, "Dark2")) 

## Term-Document
dtm <- TermDocumentMatrix(wc_data)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
d

```
